NumPy---Array Programming in Python

### 2020-02-04 body.tex
First rough re-sketch of ecosystem in Inkscape
Remove old comments
Update captions

% RG: (to discuss) this figure plus associated text says that the layers about
%     Foundation build on top of that whole foundation. In reality that's not
%     true - everything builds on NumPy, almost everything on SciPy, and very
%     little on Matplotlib/IPython/Jupyter. Perhaps "interactive environment"
%     should get its own section instead.
%     Also, I think Pandas can be added next to statsmodels as statistics. That
%     avoids explaining dataframes; now it looks like a serious omission.
%     I'd also be in favor of adding Spyder in the text; scientific computing
%     beyond exploratory work is better done in an IDE.
% KJM: agreed
% FIXME we should figure out if we want to keep working on the figures in this format or not
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights just a few of the essential tools and libraries in the vast
   scientific Python ecosystem.  Most of the ecosystem builds on NumPy arrays to
   provide a rich and powerful collection of array-aware functionality.
  }
  \label{fig:ecosystem}
\end{figure}

@@

Ideally, operating on specialized arrays using NumPy functions or semantics would
simply work, so that end users could write code once, and would then benefit
from switching between NumPy arrays, GPU arrays, distributed arrays, and so
forth, as appropriate.
To support array operations between external array objects, NumPy
therefore added the capability to act as a central coordination
mechanism with a well-specified API.

@@

  \caption{\textbf{NumPy API and Array Protocol.} Through its array protocol, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{mean} function is called on a a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:duck-arrays}

@@

To facilitate this \emph{interoperability}, NumPy provides
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions (Fig.~\ref{fig:duck-arrays}).
NumPy, in turn, dispatches operations to the originating library, as required.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   This figure highlights just a few of the essential tools and libraries in the vast
   scientific Python ecosystem.  Most of the ecosystem builds on NumPy arrays to
   provide a rich and powerful collection of array-aware functionality.
   This means that other array implementations are easily accessible to
   the ecosystem if they use the NumPy API and array protocol (Fig.~\ref{fig:array-protocol}).
  }
  \label{fig:ecosystem}
\end{figure}

@@

Ideally, operating on specialized arrays using NumPy functions or semantics would
simply work, so that end users could write code once, and would then benefit
from switching between NumPy arrays, GPU arrays, distributed arrays, and so
forth, as appropriate.
To support array operations between external array objects, NumPy
therefore added the capability to act as a central coordination
mechanism with a well-specified API (Fig.~\ref{fig:ecosystem}).

@@

  \caption{\textbf{NumPy API and Array Protocol.} Through its array protocol, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{mean} function is called on a a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:array-protocol}

@@

To facilitate this \emph{interoperability}, NumPy provides
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions (Fig.~\ref{fig:array-protocol}).
NumPy, in turn, dispatches operations to the originating library, as required.
